General purpose gene annotation using deep learning

### 2020-04-07 paper/main.tex
minor

\botrule
\end{tabular}}{Above are all parameters used during neural architecture search for the dilated CNN baseline. The same overall space was used for plant and animal data. We did, however, run multiple distinct searches that sometimes only operated over a subset of the given parameters. This was done as those seemed to be the most promising. We for example restricted the search space of the number of LSTM layers to the highest 3 values in later runs. Decisions were guided by the Genic F1 on the validation set of exactly the same data we trained our final LSTM models with. Runs with a Genic F1 below 0.5 after 10 epochs were stopped at that point and the overall maximum epoch was 15. The batch size used for almost all runs was 32 and the dilation was capped to 81. The performances seemed to be leveling of well before that. New parameters where chosen at random. The implementation and parameter space is very roughly based on (paper we looked at?) and can be found in the Helixer source code repository. In total, we ran (?) runs for the animals and (?) runs with the plant data.}
\end{table}

>>>>

\botrule
\end{tabular}}{Above are all parameters used during neural architecture search for the dilated CNN baseline. The same overall space was used for plant and animal data. We did, however, run multiple distinct searches that sometimes only operated over a subset of the given parameters. This was done as those seemed to be the most promising. We for example restricted the search space of the number of LSTM layers to the highest 3 values in later runs. Decisions were guided by the Genic F1 on the validation set of exactly the same data we trained our final LSTM models with. Runs with a Genic F1 below 0.5 after 10 epochs were stopped and the overall maximum epoch was 15. The performances seemed to be leveling off well before that. The batch size used for almost all runs was 32, the dilation was capped to 81 and the size of each fully connected layer was fixed at 128. New parameters where chosen at random. The implementation and parameter space is very roughly based on (paper we looked at?) and can be found in the Helixer source code repository. In total, we ran (?) runs for the animals and (?) runs with the plant data.}
\end{table}
